An Adolescent Mini-Neptune in the Kepler Field

### 2021-06-21 paper/ms.tex
update ms

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.9\textwidth]{f4.pdf}
			\includegraphics[width=0.9\textwidth]{f5.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf The light curve of Kepler\,1627.}
    {\it Top}: 
		The full Kepler dataset spans 1{,}437 days (3.9 years), sampled at
		30 minute cadence.  A one hundred day segment is shown here.  The {\it top panel} shows the
		\texttt{PDCSAP} median-subtracted flux in units of
		parts-per-thousand ($\times 10^{-3}$).  The dominant signal
		is induced by starspots.  The model for the
    stellar variability (orange line) is subtracted below, revealing
    the transits of \pn, as well as other deviations from the stellar
    variability model.  The Figure Set available online shows the
    entire 3.9 years of available data.
    {\it Bottom}:
		Phase-folded transit of Kepler 1627b, with stellar
			variability removed.
    The 2-$\sigma$ model uncertainties and the maximum {\it a
    posteriori} model are shown as the faint purple band, and the dark
    purple line.  Gray points are individual \texttt{PDCSAP} flux
    measurements; black points are binned to 20 minutes, with a
    representative error bar shown.
    The in-transit variation is robust against detrending methods; we
    believe it is due to starspot crossings (see text).
    \label{fig:lc}
  }
\end{figure*}

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f11.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Evidence for a prograde orbit from transit timing variations.}
    The time of each transit was measured, along with the local linear
    slope.  The two quantities are anti-correlated, which is most
    easily explained by starspot crossings during the first
    (second) half of transit inducing a positive (negative) TTV,
    provided that the orbit is prograde \citep{mazeh_time_2015}.
		\label{fig:ttvslope}
	}
\end{figure*}

>>>>

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.9\textwidth]{f4.pdf}
		}

		\subfloat{
			\includegraphics[width=0.87\textwidth]{f5.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf The light curve of Kepler\,1627.}
    {\it Top}: 
		The full Kepler dataset spans 1{,}437 days (3.9 years), sampled at
		30 minute cadence.  A one hundred day segment is shown here.  The {\it top panel} shows the
		\texttt{PDCSAP} median-subtracted flux in units of
		parts-per-thousand ($\times 10^{-3}$).  The dominant signal
		is induced by starspots.  The model for the
    stellar variability (orange line) is subtracted below, revealing
    the transits of \pn, as well as other deviations from the stellar
    variability model.  The Figure Set available online shows the
    entire 3.9 years of available data.
    {\it Bottom}:
		Phase-folded transit of Kepler 1627b, with stellar
			variability removed.
    The 2-$\sigma$ model uncertainties and the maximum {\it a
    posteriori} model are shown as the faint purple band, and the dark
    purple line.  Gray points are individual \texttt{PDCSAP} flux
    measurements; black points are binned to 20 minutes, with a
    representative error bar shown.
    The in-transit residual is robust against detrending methods; we
    believe it is caused by starspot crossings (see text).
    \label{fig:lc}
  }
\end{figure*}

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f11.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Evidence for a prograde orbit from transit timing variations.}
    The time of each transit was measured, along with the local
    slope of the light curve.  The two quantities appear anti-correlated, which is most
    easily explained by starspot crossings during the first
    (second) half of transit inducing a positive (negative) TTV,
    provided that the orbit is prograde \citep{mazeh_time_2015}.
		\label{fig:ttvslope}
	}
\end{figure*}
